A Stochastic Quasi-Newton Optimizer for TensorFlow

### 2018-05-07 paper/main.tex
Auto stash before merge of "master" and "origin/master"
Plotting rewrites and inclusion in paper
I rewrote some of the nonconvex function plot script so that it would fit better in the paper. I also added the two plots I have right now to the paper.

\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{optidef}
\usepackage{stmaryrd}
\usepackage{mathtools}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{listings}

@@

\newcommand{\RR}{\mathbb{R}}
\DeclarePairedDelimiter{\norm}{\|}{\|}
\DeclarePairedDelimiter{\ip}{\langle}{\rangle}
\DeclarePairedDelimiter{\ex}{\mathbb{E}[}{]}
\newcommand{\inv}{{}^{-1}}
\newcommand{\trans}{{}^{\top}}

@@

\begin{enumerate}
  \item Describe how TensorFlow algorithms are usually implemented.
  \item Contrast with our implementation of SdLBFGS.
  \item Explain some implementation issues.
\end{enumerate}

@@

>>>>

\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{optidef}
\usepackage[]{graphicx}
\usepackage{stmaryrd}
\usepackage{mathtools}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{listings}
\usepackage[outdir=../plots/]{epstopdf}

@@

\newcommand{\RR}{\mathbb{R}}
\DeclarePairedDelimiter{\norm}{\|}{\|}
\DeclarePairedDelimiter{\ip}{\langle}{\rangle}
\DeclarePairedDelimiter{\set}{\{}{\}}
\DeclarePairedDelimiter{\ex}{\mathbb{E}[}{]}
\newcommand{\inv}{{}^{-1}}
\newcommand{\trans}{{}^{\top}}

@@

% \begin{enumerate}
%   \item Describe how TensorFlow algorithms are usually implemented.
%   \item Contrast with our implementation of SdLBFGS.
%   \item Explain some implementation issues.
% \end{enumerate}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{../plots/nonconvex_results}
  \caption{
    SdLBFGS compared with traditional BFGS together with AdaGrad and Stochastic
    Gradient Descent on the problem $f(x) = x^6 - 2x^5 + x^3 - x^2 + 3x$, shown
    on the right. Each algorithm is initialized near the local minimum at around
    $x = 1.6$. We see that SGD, AdaGrad, and BFGS quickly converge to the local
    minimum, whereas SdLBFGS converges to the global minimum at around $x =
    -0.8$ more slowly.
  }
  \label{fig:convex-linear-system}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{../plots/linear_system_loss}
  \caption{
    SdLBFGS performance on the solving the overdetermined linear system
    $Ax = b$ with $A \in \RR^{50 \times 100}$ with convex smooth loss function
    $\norm{Ax-b}_2^2$. We sweep different memory capacity values $p \in
    \set{1,10,20,30}$ and observe that convergence is approximately equivalent
    between configurations.
  }
  \label{fig:convex-linear-system}
\end{figure}
